Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-28 mu/article/article.tex
Description completed.

$\mathcal{V}^{\mathrm{yz}}$ which has a value of -40.21374498\,Km/s for an

@@

For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.  
\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum responses for both,
We found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is
0.088\,eV.
In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
\ref{fig:up-vy-comp-rtp-1} we present the results for
fixing the polarization angle to $\alpha=40^{\circ}$ for the \emph{up} structure
vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
angles (right scale). In the bottom frames of Figs. \ref{fig:up-vx-comp-rtp-1}
and \ref{fig:up-vx-comp-rtp-1} we present the decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
corresponding $\mathcal{V}^{\mathrm{xx}}$, 
$\mathcal{V}^{\mathrm{xy}}$,
$\mathcal{V}^{\mathrm{xz}}$, and
$\mathcal{V}^{\mathrm{yx}}$, 
$\mathcal{V}^{\mathrm{yy}}$,
$\mathcal{V}^{\mathrm{yz}}$ 
components with $\alpha$ fixed to $40^{\circ}$. 

@@

@@

    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}

@@

    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The local maximum response zone is localized for an energy range
    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
    from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-2}

@@

Also there is another energy range of interest, from 1.80\,eV to 2.10\,eV and
same polarization angle $\alpha=40^{\circ}$ depicted in Fig. \ref{fig:up-3d-2},
where two local maxima are obtained the \emph{up} structure. Again, in the
bottom frame of Fig. \ref{fig:up-vx-comp-rtp-2} we have the three components
$\mathcal{V}^{\mathrm{xx}}$, $\mathcal{V}^{\mathrm{xy}}$, and
$\mathcal{V}^{\mathrm{xz}}$ corresponding to $|\mathcal{V}^{\mathrm{x}}|$ and in
the bottom frame of Fig. \ref{fig:up-vy-comp-rtp-2} the three components $\mathcal{V}^{\mathrm{yx}}$, $\mathcal{V}^{\mathrm{yy}}$, and $\mathcal{V}^{\mathrm{yz}}$ corresponding to $|\mathcal{V}^{\mathrm{y}}|$

@@

% %% Starting description of UP |V^{a}|, components and RTP

@@

We found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha = 40^{\circ}$. In the top frames of Figs. 

@@

\ref{fig:up-vab-comp-rtp-1}  and \ref{fig:up-vab-comp-rtp-2} we present the
results for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing
the polarization angle to $40^{\circ}$ for the \emph{up} structure vs the photon
energy and the corresponding polar $\varphi$ and azimuthal $\theta$ angles for
the energy range from 0.0\,eV to 0.16\,eV and from

>>>>

$\mathcal{V}^{\mathrm{yz}}$ which has a value of -40.2\,Km/s for an

@@

For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.  
\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
onset of the response is when the energy of the incoming light is the same of
the gap energy.
% 
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum zone of response for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is hold.
% 
We found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is
0.088\,eV.
%
In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present the results of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
fixing the polarization angle to $\alpha=40^{\circ}$ for the \emph{up} structure
vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
angles (right scale). In the bottom frames of same figures we present the decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
corresponding $\mathcal{V}^{\mathrm{xx}}$, 
$\mathcal{V}^{\mathrm{xy}}$,
$\mathcal{V}^{\mathrm{xz}}$, and
$\mathcal{V}^{\mathrm{yx}}$, 
$\mathcal{V}^{\mathrm{yy}}$,
$\mathcal{V}^{\mathrm{yz}}$ 
components with $\alpha$ fixed to $40^{\circ}$. 
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The local maximum response zone is localized for an energy range
    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
    from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-2}
\end{figure}

@@

Also there is another energy range of interest for an incoming energy beam from
1.80\,eV to 2.10\,eV presented in Fig. \ref{fig:up-3d-2} where two local maxima
of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ are obtained
for the \emph{up} structure resulting from evaluate Eqns. \eqref{eq:va-mag} and
\eqref{eq:vab}.
From this figure we have that for the zone between the energy ranges from
1.92\,eV to 1.94\,eV and from 1.96\,eV to 1.98\,eV and angles from $30^{\circ}$
to $45^{\circ}$ those maxima zones are hold. 
We found that the maxima are obtained when the polarization angle is fixed to
$40^{\circ}$ and the corresponding energies are 1.934\,eV and 1.972\,eV.
Again, in the top frames of Figs. \ref{fig:up-vx-comp-rtp-2} and 
\ref{fig:up-vy-comp-rtp-2} we present the results of
fixing the polarization angle to $\alpha=40^{\circ}$ vs the photon energy and
the corresponding polar $\varphi$ and azimuthal $\theta$ angles (right scale)
for the \emph{up} structure. In the bottom frames of same figures we present the
three components $\mathrm{xx}$, $\mathrm{xy}$, $\mathrm{xz}$, and $\mathrm{yx}$,
$\mathrm{yy}$, $\mathrm{yz}$ corresponding to $|\mathcal{V}^{\mathrm{x}}|$ and
$|\mathcal{V}^{\mathrm{y}}|$ fixing the polarization angle to $40^{\circ}$.

@@

    \subfigure[\ \label{fig:up-vyz-lay-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-1}}

@@

    \subfigure[\ \label{fig:up-vyz-lay-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-2}}
     \emph{up} structure.}
    \label{fig:up-vyz-lay}

@@

@@

% %% Starting description of UP |V^{x}|, components and RTP
% %% files: vab-rtp.sm_0.03_x_12802_40-spin_scissor_0_Nc_32_ang_040
% %%        alt-plots/up-vab-rtp.gp

@@

We found that for both cases, $|\mathcal{V}^{\mathrm{x}}|$ and
$|\mathcal{V}^{\mathrm{y}}|$, the corresponding components have similar
contributions and for an incoming energy beam of 1.934\,eV have values of

@@

$\mathcal{V}^{\mathrm{xx}}= 2.3$\,Km/s, 
$\mathcal{V}^{\mathrm{xy}}= 3.8$\,Km/s, 
$\mathcal{V}^{\mathrm{xz}}= 4.9$\,Km/s, and
$\mathcal{V}^{\mathrm{yx}}=11.5$\,Km/s,
$\mathcal{V}^{\mathrm{yy}}=17.0$\,Km/s,
$\mathcal{V}^{\mathrm{yz}}=20.4$\,Km/s
resulting in a in values of 
$|\mathcal{V}^{\mathrm{x}}|= 6.6$\,Km/s
$|\mathcal{V}^{\mathrm{y}}|=28.7$\,Km/s
being $|\mathcal{V}^{\mathrm{y}}|$ 4.3 times more intense than
$|\mathcal{V}^{\mathrm{x}}|$ for this photon energy. The responses have polar
and azimuthal spin polarization angels $\varphi= 42.0^{\circ}$ and $\theta=
58.7^{\circ}$ for $|\mathcal{V}^{\mathrm{x}}|$ and $\varphi= 45.2^{\circ}$ and
$\theta= 56.0^{\circ}$ for $|\mathcal{V}^{\mathrm{y}}|$.
Alike, for an incoming energy beam of 1.972\,eV all the components of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ have similar
contributions having values of
$\mathcal{V}^{\mathrm{xx}}= -5.0$\,Km/s, 
$\mathcal{V}^{\mathrm{xy}}= -5.8$\,Km/s, 
$\mathcal{V}^{\mathrm{xz}}= -6.2$\,Km/s, and
$\mathcal{V}^{\mathrm{yx}}=-26.8$\,Km/s,
$\mathcal{V}^{\mathrm{yy}}=-28.9$\,Km/s,
$\mathcal{V}^{\mathrm{yz}}=-29.7$\,Km/s
resulting in a in values of 
$|\mathcal{V}^{\mathrm{x}}|= 9.9$\,Km/s
$|\mathcal{V}^{\mathrm{y}}|=49.4$\,Km/s
being $|\mathcal{V}^{\mathrm{y}}|$ 5.0 times more intense than
$|\mathcal{V}^{\mathrm{x}}|$ for this photon energy. The responses have polar
and azimuthal spin polarization angles $\varphi=129.0^{\circ}$
$\theta=229.1^{\circ}$ or $|\mathcal{V}^{\mathrm{x}}|$ and
$\varphi=127.0^{\circ}$ and $\theta= 227.1^{\circ}$ for
$|\mathcal{V}^{\mathrm{y}}|$.
Finally we have that all the tree components of $|\mathcal{V}^{\mathrm{x}}|$ and
$|\mathcal{V}^{\mathrm{y}}|$ keep the spin polarization positive till an energy
of the incoming beam equal to 1.954\,eV when the spin polarization changes the
direction and after an energy for the incoming beam equal to 2.05\,eV both
responses goes to zero.
From the bottom frames of Figs. \ref{fig:up-vab-comp-rtp-1} and 
\ref{fig:up-vab-comp-rtp-2} we can see that for the \emph{up} structure again
the most intense component of $|\mathcal{V}^{\mathrm{x}}|$ and
$|\mathcal{V}^{\mathrm{y}}|$ corresponds to $\mathcal{V}^{\mathrm{yz}}$ which
has a value of 87.2\,Km/s for an energy incident beam of 0.088\,eV and
-29.7\,Km/s for an energy incident beam of 1.972\,eV. This component and the
corresponding layer by layer contribution is depicted in Fig. 
\ref{fig:up-vyz-lay}s.
From this figure we have that for the energy range from 0\,eV to 0.2\,eV the
response comes from the second layer composed by carbon atoms presented in Tab.
\ref{tab:up-unitcell} and denoted by the number 2 in Fig. \ref{fig:up-struc}. In
the other hand, the response for the energy range from 1.8\,eV to 2.1\,eV almost
all the response comes from the carbon atoms having a leaser contribution from
the hydrogen layer.
